### 2025-04-01 decision-making.qmd
20250401 - correct values

mdaeBracketingNotCentered1_individual <- bracketingNotCentered1[which(row.names(bracketingNotCentered1) == "crowdAveraged"), "MdAE"]
meBracketingNotCentered1_crowd <- bracketingNotCentered1[which(row.names(bracketingNotCentered1) == "crowdAveraged"), "ME"]

@@

mdaeBracketingNotCentered2_individual <- bracketingNotCentered2[which(row.names(bracketingNotCentered2) == "crowdAveraged"), "MdAE"]
meBracketingNotCentered2_crowd <- bracketingNotCentered2[which(row.names(bracketingNotCentered2) == "crowdAveraged"), "ME"]

@@

mdaeNoBracketing1_individual <- noBracketing1[which(row.names(noBracketing1) == "crowdAveraged"), "MdAE"]
meNoBracketing1_crowd <- noBracketing1[which(row.names(noBracketing1) == "crowdAveraged"), "ME"]

@@

mdaeNoBracketing2_individual <- noBracketing2[which(row.names(noBracketing2) == "crowdAveraged"), "MdAE"]
meNoBracketing2_crowd <- noBracketing2[which(row.names(noBracketing2) == "crowdAveraged"), "ME"]

@@

In conclusion, as demonstrated from these examples, when the crowd-averaged predictions are centered on the truth, the crowd-averaged predictions are perfectly accurate and are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).
When the crowd-averaged predictions bracket but are not centered on the truth, the crowd-averaged predictions are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError), but they can still be less accurate than the individual forecaster who is at the 50th percentile in accuracy.
When the crowd-averaged predictions do not bracket the truth, the crowd-averaged predictions are as accurate as the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError), but they can be less accurate than the individual forecaster who is at the 50th percentile in accuracy.

In sum, going with crowd-averaged projections will always yield predictions that are as or more accurate (in terms of [mean absolute error](#sec-meanAbsoluteError)) than the (collective) accuracy of the individuals' projections.
However, the crowd-averaged projections may be less accurate than any individual projection, including the projection of the forecaster who is at the 50th percentile in accuracy.
That is, depending on the bracketing rate, the crowd-averaged projections can still be less accurate than most individual projections.
In general, the higher the bracketing rate and the more closely that the projections are centered on the truth, the more accurate the crowd-averaged projections will be.

>>>>

mdaeBracketingNotCentered1_individual <- bracketingNotCentered1[which(row.names(bracketingNotCentered1) == "individual"), "MdAE"]
meBracketingNotCentered1_crowd <- bracketingNotCentered1[which(row.names(bracketingNotCentered1) == "crowdAveraged"), "ME"]

@@

mdaeBracketingNotCentered2_individual <- bracketingNotCentered2[which(row.names(bracketingNotCentered2) == "individual"), "MdAE"]
meBracketingNotCentered2_crowd <- bracketingNotCentered2[which(row.names(bracketingNotCentered2) == "crowdAveraged"), "ME"]

@@

mdaeNoBracketing1_individual <- noBracketing1[which(row.names(noBracketing1) == "individual"), "MdAE"]
meNoBracketing1_crowd <- noBracketing1[which(row.names(noBracketing1) == "crowdAveraged"), "ME"]

@@

mdaeNoBracketing2_individual <- noBracketing2[which(row.names(noBracketing2) == "individual"), "MdAE"]
meNoBracketing2_crowd <- noBracketing2[which(row.names(noBracketing2) == "crowdAveraged"), "ME"]

@@

In conclusion, as demonstrated from these examples, when the crowd-averaged predictions are centered on the truth, the crowd-averaged predictions are perfectly accurate and are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError) and of most individual forecasters in terms of [median absolute error](#sec-medianAbsoluteError).
When the crowd-averaged predictions bracket but are not centered on the truth, the crowd-averaged predictions are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).
If the bracketing rate is high, the crowd-averaged predictions will be more accurate—in terms of [median absolute error](#sec-medianAbsoluteError)—than most individual forecasters; however, if the bracketing rate is low, the crowd-averaged predictions can be less accurate than than most individual forecasters.
When the crowd-averaged predictions do not bracket the truth, the crowd-averaged predictions are as accurate as the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).
Depending on how far some of the individual projections are from the truth, the crowd-averaged projections can be less accurate—in terms of [median absolute error](#sec-medianAbsoluteError)—than most individual forecasters.

In sum, going with crowd-averaged projections will always yield predictions that are as or more accurate (in terms of [mean absolute error](#sec-meanAbsoluteError)) than the (collective) accuracy of the individuals' projections.
However, the crowd-averaged projections may be less accurate than any *individual* projection, including the projection of the forecaster who is at the 50th percentile in accuracy.
That is, depending on the bracketing rate, the crowd-averaged projections can still be less accurate than most individual projections.
In general, the higher the bracketing rate and the more closely that the projections are centered on the truth, the more accurate the crowd-averaged projections will be.
